### 2020-04-29 README.Rmd
Update results for all 10 cities
Close #3 for now, thanks for feedback @joeytalbot, @mem48 and @mvl22

>>>>

```{r}
roads_top = roads %>%
  filter(length > 600) %>% 
  filter(!name == "") %>% 
  arrange(desc(pctgov)) %>%
  group_by(name, ref, highway) %>% 
  summarise(pctgov = mean(pctgov), length = mean(length)) %>% 
  ungroup() %>% 
  slice(1:10) 
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_view(set.view = 12) + tm_scale_bar()
